### 2012-03-28 contents.tex
Further explanation on QA.

	Table \ref{tab:qa} presents, for each subproject, the number of developers attributed to a QA team (i.e., developers who perform verifications at least 10 times more often than contribute bug fixes), and the proportion of bug verifications they account for.
	\newcommand\MyHead[2]{%
	  \multicolumn{1}{l}{\parbox{#1}{\centering #2}}
	}

@@

>>>>

	Table \ref{tab:qa} presents, for each subproject, the number of developers attributed to a QA team (i.e., developers who perform verifications at least 10 times more often than contribute bug fixes), and the proportion of bug verifications they account for. Mass verifications and developers who have not contributed with fixes and verifications are discarded from the analysis.

	\newcommand\MyHead[2]{%
	  \multicolumn{1}{l}{\parbox{#1}{\centering #2}}
	}

@@

	Although the reported results are based on an arbitrary threshold (10) for the ratio between verifications and fixes, other values (2 and 5) were also used, leading to similar results.
